Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-27 Dissertation/Thesis/tex/ae3Dcomplex.tex
added and partly edited Section 6.2 (Mars simulation)

\section{Numerical Simulation}
% Mars simulation

\section{Experiment}
% SEH indoor simulation (needs completing)

>>>>

\section{Numerical Simulation}
In this section, we demonstrate the efficacy of the proposed 3D mapping and autonomous exploration with a simulated Mars environment. First we cover the parameters, then compare results using two different maps for entropy prediction.

\subsection{Mars Parameters}

A 3D environment of Mars is simulated in Gazebo. A height map~\cite{mapaplanet} is used to generate a contoured surface, and the corresponding picture of Mars is draped over this contour, shown in Fig. \ref{fig:MarsGazebo}. A 3D laser scanner is also simulated in Gazebo. In the horizontal direction, the sensor has limits $\Psi=120^{\circ}$ with a total of $1000$ measurement rays inside, the sensor is fixed at angle $\tilde{\psi}=45^{\circ}$, and $n_\psi=16$ sample measurements are used. In the vertical direction, the sensor also has limits $\Theta=120^{\circ}$ with a total of $1000$ measurement rays inside, but the sensor is fixed at angle $\tilde{\theta}=30^{\circ}$, and $n_\psi=7$ sample measurements are used. These ray samples are taken from each candidate location, which are separated $1$ m apart in each of the $3$ dimensions.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_heightmap.png}
        		\caption{Height Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=0.9\textwidth]{mars_colormap.png}
        		\caption{Color Map}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering{
          	\includegraphics[height=0.9\textwidth]{mars_gazebo_full_lighting.png}}
        		\caption{Gazebo Environment}
    	\end{subfigure}
\caption{The height map (a) and color map (b) are combined in the Gazebo simulator (c) to model a Mars environment. The robot captures the simulated environment to generate an occupancy grid map.}
\label{fig:MarsGazebo}
\end{figure}

The map parameters are also important to the success of the exploration. The full map has dimensions $20$ m $\times$ $20$ m $\times$ $5$ m in the Mars-fixed frame, with cell edge length $\alpha=0.075$ m. The reduced map for collision-avoidance and motion planning has cells $k=3$ times the size ($0.225$ m), so $k^3=27$ cells are considered in \refeqn{Proj3DMapComb}. The bump functions use $f_\text{max}=1.0$, $f_\text{far}=0.1$, and $\beta=0.1$ to account for travel costs with \refeqn{BumpFun}. The receding horizon optimal time $d_\text{opt}$ is based on a fixed robot velocity of $0.25$ m/sec and the computation time varies from $1.8$ sec to $2.5$ sec.

\subsection{Mars Results}

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising experimental results covered in Section \ref{sec:QuadrotorNRL}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps for Cases 1 and 2 are shown in Figs. \ref{fig:mars3DogmCase1} and \ref{fig:mars3DogmCase2}, respectively. A video of Case 1 can be found at \href{https://youtu.be/FrBcL2UMW9w}{\WriteBlue{https://youtu.be/FrBcL2UMW9w}} and close-up pictures from Case 2 are shown in Fig. \ref{fig:marsZoomedIn}. The complete map entropy is illustrated in Fig. \ref{fig:mars3Dentropy}.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap30sec.jpg}
        		\caption{$30$ sec}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap1min.jpg}
        		\caption{$1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap2min.jpg}
        		\caption{$2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap3min.jpg}
        		\caption{$3$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap4min.jpg}
        		\caption{$4$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap5min.jpg}
        		\caption{$5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap10min.jpg}
        		\caption{$10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{FullMarsMap15min.jpg}
        		\caption{$15$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{In Case 1, the robot (red disk with arrow indicating laser direction) moves toward candidate poses (red arrows, more opaque for greater reward) based on expected entropy change of the 3D probabilistic occupancy grid map $m$ (cubes: greater opacity for greater occupancy probability) of the surface of Mars.}
\label{fig:mars3DogmCase1}
\end{figure}

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap30sec.jpg}
        		\caption{$30$ sec}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap1min.jpg}
        		\caption{$1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap2min.jpg}
        		\caption{$2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap3min.jpg}
        		\caption{$3$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap4min.jpg}
        		\caption{$4$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap5min.jpg}
        		\caption{$5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap10min.jpg}
        		\caption{$10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{RdcdMarsMap15min.jpg}
        		\caption{$15$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{In Case 2, the robot (red disk with arrow indicating laser direction) generates a 3D probabilistic occupancy grid map $m$ (cubes: greater opacity for greater occupancy probability), which is used to generate a reduced map $m_\text{reduced}$ based on \refeqn{Proj3DMapComb}. The robot moves toward candidate poses (red arrows, more opaque for greater reward) based on expected entropy change of $m_\text{reduced}$. Using $m_\text{reduced}$ instead of $m$ for entropy calculation leads to faster exploration of new terrain, but this leaves some grid cells missing.}
\label{fig:mars3DogmCase2}
\end{figure}

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{mars_closeup.png}
        		\caption{Full Map Cells and Sensor Scan}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.95\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{scitech_reducedCells.png}
        		\caption{Full Map and Reduced Map Cells}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{The close-up images from the Case 2 trial show the candidate future poses (red arrows), where greater opacity represents a larger objective function of \refeqn{CandidateLocationOptimization}. In (a), we show the 3D scan with color corresponding to the surface of Mars. In (b), we overlay the full map $m$ (colored) with the reduced map $m_\text{reduced}$ (gray) from \refeqn{Proj3DMapComb}.}
\label{fig:marsZoomedIn}
\end{figure}

	\begin{figure}
		\centerline{
			\includegraphics[width=0.6\columnwidth]{scitech_entropy_comparison_flat.pdf}
		}
		\caption{The complete map entropy for Case 1 (red solid line) decreases at roughly the same rate as the reduced map entropy for Case 2 (dashed blue line) toward the beginning. However, the expected entropy in Case 2 promotes actions toward unexplored territory, while the policy of Case 1 yields a more complete map before moving on to unexplored spaces.}
		\label{fig:mars3Dentropy}
	\end{figure}

In both cases, the robot built the 3D probabilistic map of the $2000$ cubic meter space composed of $4.74\times10^6$ grid cells. The maps were mostly complete within $10$ minutes. The $\tilde{\theta}=30^{\circ}$ downward viewing angle captured the ground nicely, as candidate attitudes tended to direct the onboard sensor toward uncertain regions on the surface of Mars. The proposed approach provided collision-free mapping and autonomous exploration in real-time.

However, the choice of occupancy grid map used for entropy predictions introduced an interesting tradeoff. In Case 1, when the full probabilistic map $m$ was used in \refeqn{Iscan}, regions where the grid cells were partially-known were frequently reconsidered until the space was well-known. Conversely in Case 2, when $m_\text{reduced}$ was used instead, the robot repeatedly left spaces that were missing a few grid cells to visit new terrain. This is because $m_\text{reduced}$ contained some cells with large occupancy probabilities based on \refeqn{Proj3DMapComb}, which allowed some grid cells of $m$ enclosed within a cell of $m_\text{reduced}$ to be uncertain. The exploration policy of Case 2 incorrectly assumed these regions were well-known. Ironically, this false assumption actually led to greater information gains when the vehicle moved on to unvisited terrain. Conversely with Case $1$, which used $m$ for computing expected entropy, the total map entropy decreased more steadily and generated a more-complete 3D occupancy grid of the surface of Mars.

In short, the proposed 3D probabilistic occupancy grid mapping and autonomous exploration were simulated successfully in real-time over the surface of Mars using ROS and Gazebo. Choosing $m$ for entropy predictions produced a more-complete map, but choosing $m_\text{reduced}$ was sometimes beneficial for exploring new terrain faster, while forgoing map completeness.
